Manuscript 2: Child Health Outcomes

### 2021-12-07 papertwo_child_health.Rmd
Updating readme and some documentation

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
effects_mat$Lower <- exp(effects_mat$Estimate - 1.96*effects_mat$SE)
effects_mat$Upper <- exp(effects_mat$Estimate + 1.96*effects_mat$SE)
effects_mat$OR <- exp(effects_mat$Estimate)
effects_mat$pvalue <- pnorm(abs(effects_mat$Estimate/effects_mat$SE), lower.tail = FALSE)
effects_mat$BHPvalue <- p.adjust(effects_mat$pvalue, method="BH")

>>>>

Note: Dec. 2021

This analysis was redone using GEE, in order to meet a reviewer request for a non-Bayesian analysis and to deal with the large number of small clusters in the data.

@@

Adjusting for multiple testing:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
effects_mat$Lower <- exp(effects_mat$Estimate - 1.96*effects_mat$SE)
effects_mat$Upper <- exp(effects_mat$Estimate + 1.96*effects_mat$SE)
effects_mat$OR <- exp(effects_mat$Estimate)
effects_mat$pvalue <- pnorm(abs(effects_mat$Estimate/effects_mat$SE), lower.tail = FALSE)
effects_mat$BHPvalue <- p.adjust(effects_mat$pvalue, method="BH")
